\huge A Usability Evaluation of Tor Launcher

### 2016-10-24 pets2017-paper/pets2017-paper.tex
delete unused old text

\subsection{Connecting to Tor}

%\begin{itemize}
%	\item{Whether their Internet connection is censored} 
%	\item{Whether the Tor network is censored by their ISP}
%	\item{Which hard-coded bridges work in their country} 
%	\item{If no hard-coded bridges work, how to get a custom bridge and connect to it} 
%	\item{Whether a proxy is required to access the Internet}
%	\item{If a proxy is required, and if so, the proxy settings}
%\end{itemize}

Configuring a bridge requires providing one or more
``bridge lines,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

>>>>

\subsection{Connecting to Tor} 
Configuring a bridge requires providing one or more
``bridge lines,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.
